Supplementary Information

### 2021-01-05 doc/manuscript/MEE_manuscript_SI.Rmd
remove Hansley from Table S5
#103

\newpage
`r qualitative_results_comparison`, cont.
```{r eval = TRUE, echo=FALSE, warning=FALSE}
table_pt3 <- read.csv("tables_figures/qualitative_results_comparison.csv", 
                     colClasses=c("NULL", NA, NA, NA, NA, NA, NA), 
                     col.names=c("NULL", "species", "previously observed", "observed here", "previously observed", "observed here", "reference"), 
                     skip=breakrow2, nrows=breakrow3-breakrow2,
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt3, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(2:5, width = col_width) %>%
  column_spec(6, width = "2cm") %>%
  pack_rows("Žofín Forest Dynamics Plot, Czech Republic", 1, 4, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Niobrara and Hansley, Nebraska, USA", 5, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("Scotty Creek, NW Territories, Canada", 13, 13, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7) 
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016; @kaspar_species-specific_nodate
---
*Indicates results from a regional study including but not limited to cores from the focal site.

>>>>

\newpage
`r qualitative_results_comparison`, cont.
```{r eval = TRUE, echo=FALSE, warning=FALSE}
table_pt3 <- read.csv("tables_figures/qualitative_results_comparison.csv", 
                     colClasses=c("NULL", NA, NA, NA, NA, NA, NA), 
                     col.names=c("NULL", "species", "previously observed", "observed here", "previously observed", "observed here", "reference"), 
                     skip=breakrow2, nrows=breakrow3-breakrow2,
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt3, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(2:5, width = col_width) %>%
  column_spec(6, width = "2cm") %>%
  pack_rows("Žofín Forest Dynamics Plot, Czech Republic", 1, 4, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Niobrara, Nebraska, USA", 5, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Little Tesuque, New Mexico, USA", 6, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Cedar Breaks, Utah, USA", 8, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Scotty Creek, NW Territories, Canada", 9, 9, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7) 
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016; @kaspar_species-specific_nodate
---
*Indicates results from a regional study including but not limited to cores from the focal site.
